% REFERENCIAS

%\chapter*{REFERENCIAS}

%\chapter*{Bibliografía}
\addcontentsline{toc}{chapter}{Bibliografía}

\begin{thebibliography}{00}

\bibitem[Elect (1998)]{E_1998}  %CAP_01
Electronic Frontier Foundation (1998).
\newblock Cracking DES: Secrets of Encryption Research, Wiretap Politics \& Chip Design.
\newblock \emph{O'Reilly Media}, 1ra Ed., pp. 226.

\bibitem[Pecora y Carroll (1990)]{PyC_1990}  %CAP_01
Pecora L. M. y Carroll T. L. (1990).
\newblock Synchronization in chaotic systems.
\newblock \emph{Physical Review Letters}, \textbf{64}(8): 821-824.

\bibitem[Pecora y Carroll (1991)]{PyC_1991}  %FALTA DESCARGAR
Pecora L. M. y Carroll T. L. (1991).
\newblock Synchronizing chaotic systems.
\newblock \emph{IEEE Transactions in Circuits Systems}, \textbf{38}: 454-456.

\bibitem[Cuomo \textit{et al.} (1992)]{CEtAl_1992}  %FALTA DESCARGAR
Cuomo K. M., Oppenheim A. V. y Isabelle S. H. (1992).
\newblock Spread spectrum modulation and signal masking using synchronized chaotic system.
\newblock \emph{MIT Res. Lab. Electron.}, TR570.

\bibitem[Cuomo y Oppenheim (1992)]{CyO_1992}  %FALTA DESCARGAR
Cuomo K. M. y Oppenheim A. V. (1992).
\newblock Synchronized chaotic circuits and systems for communications.
\newblock \emph{MIT Res. Lab. Electron.}, TR575.

\bibitem[Cuomo y Oppenheim (1993)]{CyO_1993}  %FALTA DESCARGAR
Cuomo K. M. y Oppenheim A. V. (1993).
\newblock Circuit implementation of synchronized chaos with applications to communications.
\newblock \emph{Fis. Rev. Lett.}, \textbf{71}(1): 65-68.

\bibitem[Cuomo \textit{et al.} (1993)]{CEtAl_1993}  %CAP_01
Cuomo K. M., Oppenheim A. V. y Strogatz S. H. (1993).
\newblock Synchronization of Lorenz-Based Chaotic circuits with applications to communications.
\newblock \emph{IEE transactions on circuits and systems II: Analog and digital signal Processing}, \textbf{40}(10): 623-633.

\bibitem[Milanovié y Zaghloul (1996)]{MyZ_1996}  %CAP_01
Milanovié V. y Zaghloul M. E. (1996).
\newblock Improved masking algorithm for chaotic Communication systems.
\newblock \emph{Electronic Letters}, \textbf{32}(1): 11-12.

\bibitem[Gonzales \textit{et al.} (2000)]{GEtAl_2000}  %CAP_01
Gonzales O. A., Han G., Pineda de Gyvez J. y Sanchez-Sinencio E. (2000).
\newblock Lorenz-based chaotic cryptosystem: a monolithic implementation.
\newblock \emph{IEEE Transactions on Circuits and Systems I: Fundamental Theory and Applications}, \textbf{47}(8): 1243-1247.

\bibitem[Cruz-Hernández (2004)]{C_2004} 
Cruz-Hernández C. (2004).
\newblock Synchronization of time-delay Chua's oscillator with application to secure communication.
\newblock \emph{Nonlinear Dynamics and Systems Theory}, \textbf{4}(1): 1-13.

\bibitem[Posadas-Castillo \textit{et al.} (2004)]{PEtAl_2004} 
Posadas-Castillo C., Cruz-Heránndez C. y Núñez-Pérez R. F. (2004).
\newblock Experimental realization of binary signals transmission based on syncrhonized Lorenz circuits.
\newblock \emph{Journal of Applied Research and Technology}, \textbf{2}(2): 127-137.

\bibitem[López-Mancilla y Cruz-Hernández (2004)]{LyC_2004}   % FALTA DESCARGAR
López-Mancilla D. y Cruz-Hernández C. (2004).
\newblock An analysis of robustness on the synchronization of chaotic systems under nonvanishing perturbations using sliding modes.
\newblock \emph{WSEAS Transactions on Mathematics}, \textbf{3}(2): 364-369.

\bibitem[López-Mancilla y Cruz-Hernández (2005)]{LyC_2005} 
López-Mancilla D. y Cruz-Hernández C. (2005).
\newblock A note on chaos-based communication schemes.
\newblock \emph{Revista Mexicana de Física}, \textbf{51}(3): 265-269.

\bibitem[Cruz-Hernández \textit{et al.} (2005)]{CEtAl_2005} 
Cruz Hernández, C., López-Mancilla D., García-Gradilla V. J., Serrano-Guerrero H. y Núñez-Pérez R. F. (2005).
\newblock Experimental realization of binary signals transmission using chaos.
\newblock \emph{Journal of Circuit, Systems and Computer}, \textbf{14}(3): 453-468.

\bibitem[López-Mancilla \textit{et al.} (2005)]{LEtAl_2005}  % FALTA DESCARGAR
López-Mancilla D., Cruz-Hernández C. y Posadas-Castillo C. (2005).
\newblock A modified chaos-based communication scheme using hamiltonian forms and observer.
\newblock \emph{Journal of Physics: Conference Series}, \textbf{23}(23): 267-275.

\bibitem[Cruz-Hernández y Romero-Haros (2006)]{CyR_2006} % FALTA DESCARGAR
Cruz-Hernández C. y Romero-Haros N. R. (2006).
\newblock Communicating via synchronized time-delay Chuas circuits.
\newblock \emph{Communications in Nonlinear Science and Numerical Simulation}, \textbf{13}(3): 645-659.

\bibitem[Posadas-Castillo \textit{et al.} (2007)]{PEtAl_2007}  % FALTA DESCARGAR
Posadas-Castillo C., López-Gutiérrez R. M. y Cruz-Hernández C. (2007).
\newblock Synchronization of chaotic solid-state Nd:YAG lasers: Application to secure communication.
\newblock \emph{Communications in Nonlinear Science and Numerical Simulation}, \textbf{13}(8): 1655-1667.

\bibitem[Aguilar-Bustos \textit{et al.} (2008)]{AEtAl_2008a}  
Aguilar-Bustos A. Y., Cruz-Hernández C., López-Gutiérrez R. M. y Posadas-Castillo C. (2008)
\newblock Synchronization of different hyperchaotic maps for encryption.
\newblock \emph{Nonlinear Dynamics and Systems Theory}, \textbf{8}(3): 221-236.

\bibitem[López-Gutiérrez \textit{et al.} (2009)]{LEtAl_2009a}  % FALTA DESCARGAR 
López-Gutiérrez R. M., Rodríguez-Orozco E., Cruz-Hernández C., Inzunza-González E., Posadas-Castillo C., García-Guerrero E. E. y Cardoza-Avendaño L. (2009).
\newblock Secret communications using synchronized sixth-order Chuas circuits.
\newblock \emph{World Academy of Science, Engineering and Technology}, \textbf{54}(30): 608-612.

\bibitem[López-Gutiérrez \textit{et al.} (2009a)]{LEtAl_2009b}  % FALTA DESCARGAR 
López-Gutiérrez R. M., Posadas-Castillo C., López-Mancilla D. y Cruz-Hernandez C. (2009).
\newblock Communicating via robust synchronization of chaotic lasers.
\newblock \emph{Chaos, Solitons and Fractalsy}, \textbf{42}(1): 277-285.

\bibitem[Gámez-Guzmán \textit{et al.} (2009)]{GEtAl_2009}   % FALTA DESCARGAR
Gámez-Guzmán L. M., Cruz-Hernández C., López-Gutiérrez R. M. y García-Guerrero E. E. (2009).
\newblock Synchronization of Chuas circuits with multi-scroll atractors: application to communication.
\newblock \emph{Communications in Nonlinear Science and Numerical Simulation}, \textbf{14}(6): 2765-2775.

\bibitem[Serrano-Guerrero \textit{et al.} (2010)]{SEtAl_2010a}  % FALTA DESCARGAR
Serrano-Guerrero H., Cruz-Hernández C., López-Gutiérrez R. M., Posadas-Castillo C. e Inzunza-González E. (2010).
\newblock Chaotic synchronization in star coupled networks of three dimensional cellular neural networks and its application in communications.
\newblock \emph{International Journal of Nonlinear Sciences and Numerical Simulation}, \textbf{11}(8): 571-580.

\bibitem[Cardoza-Avendaño \textit{et al.} (2012)]{CEtAl_2012}
Cardoza-Avendaño L., López-Gutiérrez R. M., Cruz-Hernández C., Spirine V., Chávez-Pérez R. y Arellano-Delgado A. (2012).
\newblock Encrypted audio transmission via synchronized chaotic Nd:YAG lasers.
\newblock \emph{Revista Mexicana de Física}, \textbf{58}(6): 472-480.

\bibitem[Arellano-Delgado \textit{et al.} (2012)]{AEtAl_2012b} % FALTA DESCARGAR 
Arellano-Delgado A., López-Gutiérrez R. M., Cruz-Hernández C., Posadas-Castillo C., Cardoza-Avendaño L. y Serrano-Guerrero H. (2012).
\newblock Experimental network synchronization via plastic optical fiber.
\newblock \emph{Optical Fiber Technology}, \textbf{19}(12): 93-108.

\bibitem[Orúe \textit{et al.} (2012)]{OEtAl_2012} 
Orúe A. B., García-Mart´ínez M. J., Pastor G., Montoya F., Sánchez Ávila C. (2012).
\newblock Criptoanálisis de un criptosistema de dos canales basado en una función no lineal caótica.
\newblock \emph{XII Reunión Española sobre Criptología y Seguridad de la Información (RECSI2012) San Sebastián, España}, 119–124.

\bibitem[Wang \textit{et al.} (2004a)]{WEtAl_2004a} 
Wang X., Zhan M., Lai C.-H. y Hu G. (2004).
\newblock Error function attack of chaos synchronization based encryption schemes.
\newblock \emph{Chaos}, \textbf{14}(1): 128-137.

\bibitem[Li \textit{et al.} (2007)]{LEtAl_2007}  %CAP_01
Li S., Alvarez G., Li Z. y Halang W. A. (2007).
\newblock Analog chaos-based secure comunications and cryptanalysis: a brief survey.
\newblock \emph{PhysCon}, arXiv:0710.5455v1.

\bibitem[Zhang \textit{et al.} (2006)]{ZEtAl_2006}  %CAP_01
Zhang Y., Tao C. y Jiang J. J. (2006).
\newblock Theoretical and experimental studies of parameter estimation based on chaos feedback synchronization.
\newblock \emph{Chaos}, \textbf{16}(4): 1-8.

\bibitem[Qi \textit{et al.} (2009)]{QEtAl_2009}  %CAP_01
Qi G., Antonie van Wyk M., Jacobus van Wyk B. y Chen G. (2009).
\newblock A new hiperchaotic system and its circuit implementation.
\newblock \emph{Chaos, Solitions \& Fractals}, \textbf{40}(5): 2544-2549.

\bibitem[Pang y Liu (2011)]{PyL_2011}  %CAP_01
Pang S. y Liu Y. (2011).
\newblock A new hyperchaotic system from the Lu system and its control.
\newblock \emph{Journal of Computational and Applied Mathematics}, \textbf{235}(8): 2775-2789.

\bibitem[Kocarev (2001)]{K_2001} 
Kocarev L. (2001).
\newblock Chaos-based cryptography: A brief overview.
\newblock \emph{IEEE Circuits and Systems Magazine}, \textbf{1}(2): 6-21.

\bibitem[Yoon y Kim (2010)]{YyH_2010} % FALTA DESCARGAR
Yoon J. W. y Kim H. (2010).
\newblock An image encryption scheme with a pseudorandom permutation based on chaotic maps.
\newblock \emph{Communications in Nonlinear Science and Numerical Simulation}, \textbf{15}(12): 3998–4006.

\bibitem[Ahadpour \textit{et al.} (2012)]{AEtAl_2012} 
Ahadpour S., Sadra Y., Arasteh Fard Z. (2012).
\newblock A novel chaotic encryption scheme based on pseudorandom bit padding.
\newblock \emph{International Journal of Computer Science Issues},  \textbf{9}(1): 449-456.

\bibitem[Francois \textit{et al.} (2013)]{FEtAl_2013} 
Francois M., Grosges T., Barchiesi D. y Erra R. (2013).
\newblock A new pseudo-random number generator based on two chaotic maps.
\newblock \emph{INFORMATICA}, \textbf{24}(2): 181–197.

\bibitem[Baptista (1998)]{B_1998} 
Baptista, M. S. (1998).
\newblock Cryptography with chaos.
\newblock \emph{Physics Letters A}, \textbf{240}(1): 50-54.

\bibitem[Wang y Teng (2012)]{WyT_2012}  % FALTA DESCARGAR 
Wang X.-Y. y Teng L. (2012).
\newblock A one-time one-key encryption algorithm based on the ergodicity of chaos.
\newblock \emph{Chinese Physics B}, \textbf{21}(2): 20504-20508.

\bibitem[Asim y  Jeoti (2007)]{AyJ_2007} % FALTA DESCARGAR 
Asim M. y  Jeoti V. (2007).
\newblock Hybrid chaotic image encryption scheme based on S-box and ciphertext feedback.
\newblock \emph{International Conference on Intelligent and Advanced Systems, Kuala Lumpur, Malasia}, 25-28 noviembre de 2007, 736-741.

\bibitem[Hussaina \textit{et al.} (2014)]{HEtAl_2014} % FALTA DESCARGAR 
Hussaina I., Azama N. A. y Shaha T. (2014).
\newblock Stego optical encryption based on chaotic S-box transformation.
\newblock \emph{Optics \& Laser Technology}, \textbf{61}(6): 50–56.

\bibitem[Zhang \textit{et al.} (2014)]{ZEtAl_2014a} % FALTA DESCARGAR 
Zhang X., Mao Y. y Zhao Z. (2014).
\newblock An efficient chaotic image encryption based on alternate circular S-boxes.
\newblock \emph{Nonlinear Dynamics}, \textbf{78}(1): 359-369.

\bibitem[Mishra y Mankar (2012)]{MyM_2012} 
Mishra M. y Mankar V. H. (2012).
\newblock Message embedded cipher using 2-D chaotic map.
\newblock \emph{International Journal of Chaos, Control, Modelling and Simulation}, \textbf{1}(1): 13-24.

\bibitem[Pareek \textit{et al.} (2006)]{PEtAl_2006} 
Pareek N. K., Patidar V. y Sud K. K. (2006).
\newblock Image encryption using chaotic logistic map.
\newblock \emph{Image and Vision Computing}, \textbf{24}(9): 926-934.

\bibitem[Patidar \textit{et al.} (2009)]{PEtAl_2009} 
Patidar V., Pareek N. K. y Sud K. K. (2009).
\newblock A new substitution-diffusion based image cipher using chaotic standard and logistic maps.
\newblock \emph{Commun Nonlinear Sci Numer Simulat}, \textbf{14}(7): 3056-3075.

\bibitem[Hongjun y Xingyuan (2010)]{HyX_2010} 
Hongjun L. y Xingyuan W. (2010).
\newblock Color image encryption based on one-time keys and robust chaotic maps.
\newblock \emph{Computers and Mathematics with Applications}, \textbf{59}(10): 3320-3327.

\bibitem[Cui (2010))]{C_2010} 
Cui D. (2010).
\newblock A novel fingerprint encryption algorithm based on chaotic system and fractional fourier transform.
\newblock \emph{IEEE International Conference on Machine Vision and Human-machine Interface}, 168-171.

\bibitem[Chen y Chang (2011)]{CyC_2011} 
Chen D. y Chang Y. (2011).
\newblock A novel image encryption algorithm based on logistic maps.
\newblock \emph{Advances in Information Sciences and Service Sciences}, \textbf{3}(7): 364-372.

\bibitem[Wang \textit{et al.} (2012)]{WEtAl_2012} 
Wang X., Teng L. y Qin X. (2012).
\newblock A novel colour image encryption algorithm based on chaos.
\newblock \emph{Signal Processing}, \textbf{92}(4): 1101-1108.

\bibitem[Liu (2012)]{L_2012} 
Liu R. (2012).
\newblock Chaos-based fingerprint images encryption using symmetric cryptography.
\newblock \emph{9th International Conference on Fuzzy Systems and Knowledge Discovery}, pp. 2153-2156.

\bibitem[Inzunza-Gonz\'alez y Cruz-Hern\'andez (2013)]{IyC_2013} 
Inzunza-Gonz\'alez E. y Cruz-Hern\'andez C. (2013).
\newblock Double hyperchaotic encryption for security in biometric systems.
\newblock \emph{Nonlinear Dynamics and Systems Theory}, \textbf{13}(1): 55-68.

\bibitem[Naeem \textit{et al.} (2014)]{NEtAl_2014} 
Naeem E. A., Abd Elnaby M. M., Soliman N. F., Abbas A. M., Faragallah O. S., Semary N., Hadhoud M. M.,  Alshebeili S. A. y Abd El-Samie F. E. (2014).
\newblock Efficient implementation of chaotic image encryption in transform domains.
\newblock \emph{The Journal of Systems and Software}, \textbf{97}(7): 118–127.

\bibitem[Khurram Khan \textit{et al.} (2007)]{KEtAl_2007} 
Khurram Khan M., Zhang J. y Tian L. (2007).
\newblock Chaotic secure content-based hidden transmission of biometric templates.
\newblock \emph{Chaos, Solitons and Fractals}, \textbf{32}(5): 1749-1759.

\bibitem[Xiaomin \textit{et al.} (2011)]{XEtAl_2011} 
Xiaomin W., TaiHua Xu y Wenfang Z. (2011).
\newblock Chaos-based biometrics template protection and secure authentication.
\newblock \emph{State of the Art in Biometrics}, Dr. Jucheng Yang (Ed.), pp. 293-314.

\bibitem[Wang \textit{et al.} (2005)]{WEtAl_2005} 
Wang K., Pei W., Zou L., Song A. y He Z. (2005).
\newblock On the security of 3D Cat map based symmetric image encryption scheme.
\newblock \emph{Physics Letters A}, \textbf{343}(6): 432-439.

\bibitem[Wang \textit{et al.} (2007)]{WEtAl_2007} 
Wang Y., Liao X., Xiang T., Wong K.-W. y Yang D. (2007).
\newblock Cryptanalysis and improvement on a block cryptosystem based on iteration a chaotic map.
\newblock \emph{Physics Letters A}, \textbf{363}(4): 277-281.

\bibitem[Balaji y Nagaraj (2008)]{ByN_2008} 
Balaji N. y Nagaraj N. (2008).
\newblock Cryptanalysis of a chaotic image encryption algorithm.
\newblock \emph{National Conference on Nonlinear Systems and Dynamics}, arXiv:0801.0276, pp. 1-14.

\bibitem[Cokal y Solak (2009)]{CyS_2009} 
Cokal C. y Solak E. (2009).
\newblock Cryptanalysis of a chaos-based image encryption algorithm.
\newblock \emph{Physics Letters A}, \textbf{373}(15): 1357-1360.

\bibitem[Alvarez y Li (2009)]{AyL_2009} 
Alvarez G. y Li S. (2009).
\newblock Cryptanalyzing a nonlinear chaotic algorithm (NCA) for image encryption.
\newblock \emph{Commun Nonlinear Sci Numer Simulat}, \textbf{14}(11): 3743-3749.

\bibitem[Li \textit{et al.} (2009)]{LEtAl_2009} 
Li C., Chen G. y Halang W. A. (2009).
\newblock Cryptanalysis of an image encryption scheme based on a compound chaotic sequence.
\newblock \emph{Image and Vision Computing}, \textbf{27}(8): 1035-1039.

\bibitem[Rhouma \textit{et al.} (2010)]{REtAl_2010} 
Rhouma R., Solak E. y Belghith S. (2010).
\newblock Cryptanalysis of a new substitution-diffusion based image cipher.
\newblock \emph{Commun Nonlinear Sci Numer Simulat}, \textbf{15}(7): 1887-1892.

\bibitem[Solak \textit{et al.} (2010)]{SEtAl_2010} 
Solak E., Cokal C., Yildiz O. T. y Biyikiglu T. (2010).
\newblock Cryptoanalysis of Fridrich's chaotic image encryption.
\newblock \emph{International Journal of Bifurcation and Chaos}, \textbf{20}(5): 1405-1413.

\bibitem[Li \textit{et al.} (2011)]{LEtAl_2011} 
Li C., Li S. y Lo K.-T. (2011).
\newblock Breaking a modified substitution-diffusion image cipher based on chaotic standard and logistic maps.
\newblock \emph{Commun Nonlinear Sci Numer Simulat}, \textbf{16}(2): 837-843.

\bibitem[Zhang \textit{et al.} (2011)]{ZEtAl_2011} 
Zhang Y., Li C., Li Q., Zhang D. y Shum S. (2011).
\newblock Breaking a chaotic image encryption algorithm based on perceptron model.
\newblock \emph{Nonlinear Dynamics}, \textbf{69}(3): 1091-1096.

\bibitem[Li \textit{et al.} (2012)]{LEtAl_2012} 
Li C., Zhang Y., Ou R. y Wong K.-W. (2012).
\newblock Breaking a novel colour image encryption algorithm based on chaos.
\newblock \emph{Nonlinear Dynamics}, \textbf{70}(4): 2383-2388.

\bibitem[Arroyo \textit{et al.} (2009)]{AEtAl_2009} 
Arroyo D., Alvarez G. y Li S. (2009).
\newblock Some Hints for the Design of Digital Chaos-Based Cryptosystems: Lessons Learned from Cryptanalysis.
\newblock \emph{Conference on Analysis and Control of Chaotic Systems}, pp. 171-175.

\bibitem[Shannon (1948)]{S_1948}
Shannon, C. E. (1949).
\newblock A mathematical theory of communication.
\newblock \emph{The Bell System Technical Journal}, \textbf{27}: 379–423.

\bibitem[Shannon (1949)]{S_1949}
Shannon, C. E. (1949).
\newblock Communication theory of secrecy systems.
\newblock \emph{The Bell System Technical Journal}, \textbf{28}: 656-715.

\bibitem[Brown y Chua (1996)]{ByC_1996}
Brown R. y Chua L. O. (1996).
\newblock Clarifying chaos: examples and counterexamples.
\newblock \emph{International Journal of Bifurcation and Chaos}, \textbf{6}(2): 219–249.

\bibitem[Fridrich (1998)]{F_1998}  % FALTA DESCARGAR 
Fridrich J. (1998).
\newblock Symmetric ciphers based on two-dimensional chaotic maps.
\newblock \emph{Int. J. Bifurcation Chaos}, \textbf{8}(6): 1259.

\bibitem[Alvarez \textit{et al.} (1999)]{AEtAl_1999}  % FALTA DESCARGAR 
Alvarez G., Montoya F., Pastor G. y Romera M. (1999).
\newblock Chaotic cryptosystems.
\newblock \emph{International Carnahan Conference on Security Technology, Madrid, España}, 5-7 de octubre de 1999, 332-338.

\bibitem[Petitcolas (2011)]{P_2011} % FALTA DESCARGAR
Petitcolas F.A.P. (2011).
\newblock Kerckhoffs’ Principle.
\newblock \emph{Encyclopedia of Cryptography and Security}, 2da Ed., pp. 675.

\bibitem[Ott (1993)]{O_1993}  %CAP_01
Ott E. (1993).
\newblock Chaos in dynamical systems.
\newblock \emph{Cambridge University Press}, 1ra Edición, pp. 385.

\bibitem[Hilborn (2005)]{H_2005}  %CAP_01
Hilborn R. C. (2005).
\newblock Chaos and nonlinear dynamics: An introduction for scientists and engineering.
\newblock \emph{OXFORD University Press}, 2da Edición, pp. 672.

\bibitem[Lorenz (1963)]{L_1963}  %CAP_02
Lorenz E. N. (1963).
\newblock Deterministic nonperiodic flow.
\newblock \emph{Journal of the atmospheric science}, \textbf{20}(2): 130-142.

\bibitem[Wolf (1986)]{W_1986}  %CAP_02
Wolf A. (1986).
\newblock Quantifying chaos with Lyapunov exponents.
\newblock \emph{Chaos}, Princeton University Press, cap. 13, pp.273-289.

\bibitem[Sprott (2003)]{S_2003}  %CAP_02
Sprott J. C. (2003).
\newblock Lyapunov exponents.
\newblock \emph{Chaos and time-series analysis}, Oxford University Press, cap. 5.

\bibitem[May (1976)]{M_1976}  %CAP_02
May R. M. (1976).
\newblock Simple mathematical models with very complicated dynamics.
\newblock \emph{Nature}, \textbf{261}(5560): 459-467.

\bibitem[Granados (2006)]{G_2006}
Granados, G. (2006).
\newblock Introducción a la criptografía.
\newblock \emph{Revista Digital Universitaria}, \textbf{7}(7): 1-17.

\bibitem[Kotulsk y Szczepañski (1997)]{KyS_1997}
Kotulsk Z. y Szczepañski J. (1997).
\newblock Discrete chaotic cryptography.
\newblock \emph{Proc. NEEDS 1997}, 1–11.

\bibitem[Alvarez y Li (2006)]{AyL_2006}  
Alvarez G. y Li S. (2006).
\newblock Some basic cryptographic requirements for chaos-based cryptosystems.
\newblock \emph{International Journal of Bifurcation and Chaos}, \textbf{16}(8): 2129-2151.

\bibitem[Menezes \textit{et al.} (1996)]{MEtAl_1996}
Menezes A., van Oorschot P. y Vanstone S. (1996).
\newblock Pseudorandom Bits and Sequences.
\newblock \emph{Handbook of Applied Cryptography}, CRC Press, cap. 5, pp. 169-190.

\bibitem[FIPS 140-1 (1994)]{FIPS_1994}
FIPS 140-1 U.S. Department of Commerce / National Institute of Standards and Technology (1994).
\newblock Security requirements for cryptographic modules FIPS 140-1.
\newblock \emph{Federal Information Processing Standards Publication}, FIPS 140-1.

\bibitem[FIPS 140-2 (2001)]{FIPS_2001}
FIPS 140-2 U.S. Department of Commerce / National Institute of Standards and Technology (2001).
\newblock Security requirements for cryptographic modules FIPS 140-2.
\newblock \emph{Federal Information Processing Standards Publication}, FIPS 140-2.

\bibitem[MCF5225X (2008)]{F_2008}
MCF5225X Freescale Semiconductor (2008).
\newblock MCF5225x Family.
\newblock \emph{Freescale Semiconductor}, KRN3MCF5225XFS/REV 2.

\bibitem[Aboul-Seoud \textit{et al.} (2011)]{A-SEtAl_2011}  %CAP_05 
Aboul-Seoud A. K., El-Badawy E. A., Mokhtar A., El-Marsy W., El-Barbry M. y El-Din Sayed Hafez A. (2011).
\newblock A simple 8 bit digital microcontroller implementation for chaotic sequence generation.
\newblock \emph{28th National Radio Science Conference, National Telecomunication Institute, Cairo, Egipto}, 26-28 abril de 2011, 1-9.

\bibitem[Serna y Joshi (2011)]{SyJ_2011}   %CAP_05
Serna J. D. y Joshi A. (2011).
\newblock Visualizing the logistic map with a microcontroller.
\newblock \emph{Physics Education}, \textbf{47}(6): 1-6.

\bibitem[Volos (2013)]{V_2013}  %CAP_05 
Volos C. K. (2013).
\newblock Chaotic random bit generator realized with a microcontroller.
\newblock \emph{Journal of Computations \& Modelling}, \textbf{3}(4): 115-136.

\bibitem[Chiu \textit{et al.} (2013)]{CEtAl_2013}  %CAP_05 
Chiu R., Mora-González M. y López-Mancilla D. (2013).
\newblock Implementation of a chaotic oscillator into a simple microcontroller.
\newblock \emph{IERI Procedia}, \textbf{4}, 247-252.

\bibitem[Stanciu y Datcu (2012)]{SyD_2012} 
Stanciu M. y Datcu O. (2012).
\newblock Atmel AVR microcontroller implementation of a new enciphering algorithm based on a chaotic generalized Hénon map.
\newblock \emph{9th International Conference on Communications, Bucharest, Rumania}, 21-23 junio de 2012, 319-322.

\bibitem[Andreatos y Volos (2014)]{AyV_2014} 
Andreatos A. S. y Volos C. K. (2014).
\newblock Secure text encryption based on hardware chaotic noise generator.
\newblock \emph{2nd International Conference on Cryptography and Its Applications in the Armed Forces, Atenas, Grecia}, 2 de abril del 2014.

\bibitem[Zidan (2011)]{ZEtAl_2011a}  
Zidan M. A., Radwan A. G. y Salama K. N. (2011).
\newblock The effect of numerical techniques on differential equation based chaotic generators.
\newblock \emph{IEEE International Conference on Microelectronics, Hammamet, Túnez}, 19-22 diciembre de 2011, 1-4.

\bibitem[Yang \textit{et al.} (2005)]{YEtAl_2005}  %CAP_05 
Yang W. Y., Cao W., Chung T. y Morris J. (2005).
\newblock Aplied numerical methods using Matlab.
\newblock \emph{Wiley-Interscience}, 509 páginas.

\bibitem[Arroyo \textit{et al.} (2008)]{AEtAl_2008}  
Arroyo D., Alvarez G. y Fernandez V. (2008).
\newblock On the inadequacy of the logistic map for cryptographic applications.
\newblock \emph{X Reunión Española sobre Criptología y Seguridad de la Información}, 77-82.

\bibitem[Cristian-Iulian y Vasile-Gabriel (2017)]{CyV_2017}  
Cristian-Iulian R. y Vasile-Gabriel I. (2017).
\newblock Aspects regarding chaotic maps hardware implementations.
\newblock \emph{Revue Roumaine Des Sciences Techniques}, \textbf{52}(2): 219-227.

\bibitem[Zhou \textit{et al.} (2012)]{ZEtAl_2012}  
Zhou S, Zhang Q., Wei X. y Zhou C. (2012).
\newblock A summarization of image encryption.
\newblock \emph{IETE Technical Review}, \textbf{27}(6): 503-510.

\bibitem[Dang y Chau (2000)]{DyC_2000}  
Dang P. P. y Chau P. M. (2000).
\newblock Image encryption for secure internet multimedia applications.
\newblock \emph{International Journal of Computer Science \& Engineering}, \textbf{46}(3): 396-403.

\bibitem[Chen \textit{et al.} (2004)]{CEtAl_2004}  
Chen G., Mao Y. y Chui C. K. (2004).
\newblock A symmetric image encryption scheme based on 3D chaotic cat maps.
\newblock \emph{International Journal of Computer Science \& Engineering}, \textbf{21}(3): 749-761.

\bibitem[Zeghid \textit{et al.} (2007)]{MEtAl_2007}  
Zeghid M., Machhout M., Khriji L., Baganne A. y Tourki R. (2007).
\newblock A modified AES based algorithm for image encryption.
\newblock \emph{International Journal of Computer, Information, Systems and Control Engineering}, \textbf{1}(3): 726-731.

\bibitem[Muhaya \textit{et al.} (2009)]{MEtAl_2009}  
Muhaya F. B., Usama M. y Khan M. K. (2009).
\newblock Modified AES using chaotic key generator for satellite imagery encryption.
\newblock \emph{Emerging Intelligent Computing Technology and Applications}, \textbf{5754}: 1014-1024.

\bibitem[Wong \textit{et al.} (2008)]{WEtAl_2008}  
Wong K.-W., Kwok S.-H. y Law W.-S. (2008).
\newblock A fast image encryption scheme based on chaotic standard map.
\newblock \emph{Physics Letters A}, \textbf{372}(15): 2645–2652.

\bibitem[Usamaa  \textit{et al.} (2010)]{UEtAl_2010}  
Usamaa M., Khana M. K., Alghathbar K. y Lee C. (2010).
\newblock Chaos-based secure satellite imagery cryptosystem.
\newblock \emph{Computers and Mathematics with Applications}, \textbf{60}(2): 326-337.

\bibitem[Wang \textit{et al.} (2010)]{WEtAl_2010}  
Wang X., Yang L., Liu R. y Kadir A. (2010).
\newblock A chaotic image encryption algorithm based on perceptron model.
\newblock \emph{Nonlinear Dynamics}, \textbf{62}(3): 615-621.

\bibitem[Tong y Cui (2008)]{TyC_2008}  
Tong X. y Cui M. (2008).
\newblock Image encryption with compound chaotic sequence cipher shifting dynamically.
\newblock \emph{Image and Vision Computing}, \textbf{26}(6): 843-850.

\bibitem[Feng \textit{et al.} (2006)]{FEtAl_2006}  
Feng Y., Li L. y Huang F. (2006).
\newblock A symmetric image encryption approach based on line maps.
\newblock \emph{1st International Symposium on Systems and Control in Aerospace and Astronautics, Harbin, República Popular China}, 19-21 junio de 2006, 1367.

\bibitem[Gao \textit{et al.} (2006)]{GEtAl_2006}  
Gao H., Zhang Y., Liang S. y Li D. (2006).
\newblock  A new chaotic algorithm for image encryption.
\newblock \emph{Chaos, Solitons \& Fractals}, \textbf{29}: 393-399.

\bibitem[Xiang \textit{et al.} (2006)]{XEtAl_2006}  
Xiang T., Liao X., Tang G., Chen Y. y Wong K.-W. (2006).
\newblock A novel block cryptosystem based on iterating a chaotic map.
\newblock \emph{Physics Letters A}, \textbf{349}(1): 109-115.

\bibitem[Guan \textit{et al.} (2005)]{GEtAl_2005}  
Guan Z.-H., Huang F. y Guan W. (2005).
\newblock Chaos-based image encryption algorithm.
\newblock \emph{Physics Letters A}, \textbf{346}(1): 153-157.

\bibitem[Patidar \textit{et al.} (2010)]{PEtAl_2010}  
Patidar V., Pareek N. K., Purohit G. y Sud K. K. (2010).
\newblock Modified substitution-diffusion image cipher using chaotic standard and logistic maps.
\newblock \emph{Commun Nonlinear Sci Numer Simulat}, \textbf{15}(10): 2755-2765.

\bibitem[Zhang \textit{et al.} (2013)]{ZEtAl_2013}  
Zhang W., Wong K.-W., Yu H. y Zhu Z.-L. (2013).
\newblock An image encryption scheme using reverse 2-dimensional chaotic map and dependent diffusion.
\newblock \emph{Commun Nonlinear Sci Numer Simulat}, \textbf{18}(8): 2066-2080.

\bibitem[Bakhshandeh y Eslami (2013)]{ByE_2013}  
Bakhshandeh A. y Eslami Z. (2013).
\newblock An authenticated image encryption scheme based on chaotic maps and memory cellular automata.
\newblock \emph{Optics and Lasers in Engineering}, \textbf{51}(6): 665-673.

\bibitem[Fu \textit{et al.} (2013)]{FEtAl_2013a}  
Fu C., Hou S., Zhou W., Liu W.-Q. y Wang D.-L. (2013).
\newblock A chaos-based image encryption scheme with a plaintext related diffusion.
\newblock \emph{9th Int. Conf. on Information, Communications and Signal Processing, Tainan, República de China}, 10-13 de diciembre de 2013,1-5.

\bibitem[Zhu (2012)]{Z_2012}  
Zhu C. (2012).
\newblock A novel image encryption scheme based on improved hyperchaotic sequences.
\newblock \emph{Optics Communications}, \textbf{285}(1): 29-37.

\bibitem[Wang y Yu (2009)]{WyY_2009}  
Wang X. y Yu C. (2009).
\newblock Cryptanalysis and improvement on a cryptosystem based on a chaotic map.
\newblock \emph{Computers and Mathematics with Applications}, \textbf{57}(3): 476-482.

%100
\bibitem[Zhou \textit{et al.} (2014)]{ZEtAl_2014}  
Zhou Y., Bao L. y Philip Chen C. L. (2014).
\newblock A new 1D chaotic system for image encryption.
\newblock \emph{Signal Processing}, \textbf{97}(1): 172-182.

\bibitem[Liu \textit{et al.} (2012)]{LEtAl_2012a}  
Liu L., Zhang Q. y Wei X. (2012).
\newblock A RGB image encryption algorithm based on DNA encoding and chaos map.
\newblock \emph{Computers and Electrical Engineering}, \textbf{38}(5): 1240-12481.

\bibitem[Liu (2014)]{L_2014}  
Liu Y. (2014).
\newblock Cryptanalyzing a rgb image encryption algorithm based on dna encoding and chaos map.
\newblock \emph{Optics and Laser Technology}, \textbf{60}: 111-115.

\bibitem[FIPS PUB 46-3 (1999)]{FIPS46_1999}  
FIPS PUB 46-3 (1999).
\newblock Data encryption standard (DES).
\newblock \emph{National Institute of Standards and Technology}, http://csrc.nist.gov/publications/fips/archive/fips46-3/fips46-3.pdf

\bibitem[FIPS PUB 197 (2001)]{FIPS197_2001}  
FIPS PUB 197 (2001).
\newblock Advanced encryption standard (AES).
\newblock \emph{National Institute of Standards and Technology}, http://csrc.nist.gov/publications/fips/fips197/fips-197.pdf

\bibitem[Ferguson {et al.} (2001)]{FEtAl_2001}  
Ferguson N., Schroeppel R. y Whiting D. (2001).
\newblock A simple algebraic representation of Rijndael.
\newblock \emph{Lecture Notes in Computer Science}, \textbf{2259}: 103-111.

\bibitem[Adleman (1994)]{A_1994}  
Adleman L. M. (1994)
\newblock Molecular computation of solution to combinatorial problems.
\newblock \emph{Science}, \textbf{266}(5187): 1021-2024.

\bibitem[Guozhen \textit{et al.} (2006)]{GEtAl_2006a} 
Guozhen X., Mingxin L., Lei Q. y Xuejia L. (2006)
\newblock New field of cryptography: DNA cryptography.
\newblock \emph{Chinese Science Bulletin}, \textbf{51}(12): 1413-1420.

\bibitem[Bordoa y Tornea (2010)]{ByT_2010} 
Bordoa M. y Tornea O. (2010)
\newblock DNA secret writing techniques.
\newblock \emph{8th International Conference on Communications}, pp. 451-456.

\bibitem[XueJia \textit{et al.} (2010)]{XEtAl_2010} 
XueJia L., MingXin L., Lei Q., JunSong H. y XiWen F. (2010)
\newblock Asymmetric encryption and signature method with DNA technology.
\newblock \emph{Science China Information Sciences}, \textbf{53}(3): 506-514.

\bibitem[Abbasy \textit{et al.} (2011)]{AEtAl_2011} 
Abbasy M.R., Manaf A.A. y Shahidan M.A. (2011)
\newblock Data Hiding Method Based on DNA Basic Characteristics.
\newblock \emph{Communications in Computer and Information Science}, \textbf{194}: 53-62.

\bibitem[Liu \textit{et al.} (2013)]{LEtAl_2013a} 
Liu H., Lin D. y Kadir A. (2013)
\newblock A novel data hiding method based on deoxyribonucleic acid coding.
\newblock \emph{Computers and Electrical Engineering}, \textbf{39}(4): 1164-1173.

\bibitem[Fournaris y Sklavos (2014)]{FyS_2014}  
Fournaris A.P. y Sklavos N. (2014)
\newblock Secure embedded system hardware design: a flexible security and trust enhanced approach.
\newblock \emph{Computers and Electrical Engineering}, \textbf{40}(1): 121–133.

\bibitem[MCF52259RM (2009)]{M52259_2009} 
MCF52259RM.
\newblock MCF52259 ColdFire integrated microcontroller reference manual.
\newblock \emph{MCF52259RM} 2009;Rev. 2 8/2009.

\bibitem[Jain y Uludag (2003)]{JyU_2003} 
Jain A.K. and Uludag U. (2003).
\newblock Hiding biometric data.
\newblock \emph{IEEE Transactions on Pattern Analysis and Machine Intelligence}, \textbf{25}(11): 1494-1498.

\bibitem[Soutar \textit{et al.} (1999)]{SEtAl_1999} 
Soutar C., Roberge D., Stoianov A., Gilroy R. y Vijaya Kumar B.V.K. (1999).
\newblock Biometric encryption.
\newblock \emph{ICSA Guide to Cryptography}, McGraw-Hill.

\bibitem[Ratha \textit{et al.} (2001)]{REtAl_2001} 
Ratha N.K., Connell J.H. y Bolle R.M. (2001).
\newblock An analysis of minutiae matching strength.
\newblock \emph{Lecture Notes in Computer Science}, \textbf{2091}: 223-228.

\bibitem[Prasad y Kumar (2014)]{PyK_2014} 
Prasad M.V.N.K. y Kumar C.S. (2014).
\newblock Fingerprint template protection using multiline neighboring relation.
\newblock \emph{Expert Systems with Applications}, \textbf{41}(14):  6114–6122.

\bibitem[Jin \textit{et al.} (2012)]{JEtAl_2012} 
Jin Z., Beng Jin Teoh A., Song Ong T. y Tee C. (2012).
\newblock Fingerprint template protection with minutiae-based bit-string for security and privacy preserving.
\newblock \emph{Expert Systems with Applications}, \textbf{39}(6): 6157–6167.

\bibitem[Kevenaar \textit{et al.} (2010)]{KEtAl_2010} 
Kevenaar T., Korte U., Merkle J., Niesing M, Ihmor H., Busch C. y Zhou X. (2010).
\newblock A reference framework for the privacy assessment of keyless biometric template protection systems.
\newblock \emph{In Proceedings of BIOSIG, Darmstadt, Alemania}, 9-10 de septiembre de 2010, 45-56.

\bibitem[Nandakumar \textit{et al.} (2007)]{NEtAl_2007} 
Nandakumar K., Nagar A. y Jain A.K. (2007).
\newblock Hardening fingerprint fuzzy vault using password.
\newblock \emph{Lecture Notes in Computer Science} \textbf{4642}: 927-937.

\bibitem[Chen y Dai (2005)]{CyD_2005} 
Chen C.-H. y Dai J.-H. (2005).
\newblock An embedded fingerprint authentication system with reduced hardware resources requirement.
\newblock \emph{Proceedings of the Ninth International Symposium on Consumer Electronics}, 14-16 de junio de 2005, 145-150.

\bibitem[Nayak (2008)]{N_2008} 
Nayak D.R. (2008).
\newblock A novel architecture for embedded biometric authentication system.
\newblock \emph{European Symposium on Computer Modeling and Simulation, Liverpool, Amsterdam, Inglaterra}, 8-10 de septiembre de 2008, 567-572.

\bibitem[Militello \textit{et al.} (2008)]{MEtAl_2008} 
Militello C., Conti V., Vitabile S. y Sorbello F. (2008).
\newblock A novel embedded fingerprints authentication system based on singularity points.
\newblock \emph{International Conference on Complex, Intelligent and Software Intensive Systems, Barcelona, España}, 4-7 de marzo de 2008, 72-78.

\bibitem[Nie \textit{et al.} (2013)]{NEtAl_2013} 
Nie T., Li Y., Zhou L. y Toyonaga M. (2013).
\newblock A multilevel fingerprinting method for FPGA IP protection.
\newblock \emph{IEEE International Symposium on Circuits and Systems, Beijing, China}, 19-23 de mayo de 2013, 1789-1792.

\bibitem[Fons \textit{et al.} (2007)]{FEtAl_2007}  
Fons M., Fons F. y Cant\'o E. (2007).
\newblock Embedded security: new trends in personal recognition systems.
\newblock \emph{Research in Microelectronics and Electronics Conference, Bordeaux, Francia}, 2-5  de julio de 2007, 89-92.

\bibitem[Wang \textit{et al.} (2004)]{WEtAl_2004} 
Wang Y., Li D., Isshiki T. y Kunieda H. (2004).
\newblock A novel SOC architecture embedded bit serial FPGA.
\newblock \emph{IEEE Conference on Circuits and Systems}, \textbf{1}: 133-136.

\bibitem[Roberts (2007)]{R_2007} 
Roberts C. (2007).
\newblock Biometric attack vectors and defences.
\newblock \emph{Computers and Security}, \textbf{26}(1): 14-25.

\bibitem[Luis-García \textit{et al.} (2003)]{LGEtAl_2003} 
Luis-García R. de, Alberola-López C., Aghzout O. y Ruiz-Alzola J. (2003).
\newblock Biometric identification systems.
\newblock \emph{Signal Processing}, \textbf{83}(12): 2539-2557.

\bibitem[141]{FS83}
Futronic.
\newblock Futronic FS83C PIV serial Fingerprint Authentication Module(sFAM).
\newblock \emph{Futronic Technology Company Limited}, http://www.futronic-tech.com/download/FS83C/brochure.pdf.


\end{thebibliography}